Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
chore: refiniments

%where $\pi = \{\pi^i\}_{i \in N}$ represents the joint policy. 
%The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
There are several algorithms which try to find the optimal Q-value function, one of the most popular is the deep Q-learning algorithm.
\subsubsection{Deep Q-Learning Formalization}
deep Q-learning utilizes a deep neural network, 
often referred to as a Q-network, to approximate the action-value function $Q(s, a)$. 
This network takes the state $s$ as input and outputs a vector of Q-values, one for each possible action $a \in \mathcal{A}$.  
The optimal action-value function, denoted $Q^*(s, a)$, satisfies the Bellman optimality equation:

@@

where $\theta$ are the parameters of the Q-network, $\theta^-$ are the parameters of a target Q-network (used for stability), 
and $\mathcal{D}$ is the experience replay buffer, a collection of past experiences $(s, a, r, s')$.
%
In the multi-agent setting, each agent $i$ has its own Q-network $Q^i(o^i, a^i; \theta^i)$ that takes its local observation $o^i$ as input.  
For centralized training, the global state $s$ can be used as input. 
The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., independent Q-learning, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).  
For example, in independent deep Q-learning, each agent updates its Q-network independently using its local reward $r^i$:
\begin{equation}
  \resizebox{\linewidth}{!}{$
  \mathcal{L}^i(\theta^i) = \mathbb{E}_{(o^i, a^i, r^i, o'^i) \sim \mathcal{D}^i} \left[ \left( r^i + \gamma \max_{a'^i} Q^i(o'^i, a'^i; \theta^{i-}) - Q^i(o^i, a^i; \theta^i) \right)^2 \right]
  $}
  \end{equation}
%\subsection{Key Concepts}

>>>>

%where $\pi = \{\pi^i\}_{i \in N}$ represents the joint policy. 
%The goal in collaborative MARL is often to find a joint policy that maximizes this global average Q-value or a similar global objective.
There are several algorithms which try to find the optimal Q-value function, one of the most popular is the deep Q-learning algorithm.
\subsubsection{Deep Q-Learning Formalization}
Deep Q-learning~\cite{DBLP:conf/l4dc/FanWXY20} utilizes a deep neural network, 
often referred to as a Q-network, to approximate the action-value function $Q(s, a)$. 
This network takes the state $s$ as input and outputs a vector of Q-values, one for each possible action $a \in \mathcal{A}$.  
The optimal action-value function, denoted $Q^*(s, a)$, satisfies the Bellman optimality equation:

@@

where $\theta$ are the parameters of the Q-network, $\theta^-$ are the parameters of a target Q-network (used for stability), 
and $\mathcal{D}$ is the experience replay buffer, a collection of past experiences $(s, a, r, s')$.
%
In the multi-agent setting, each agent $i$ has its own Q-network $Q^i(o^i, a^i; \theta^i)$ that takes its local observation $o^i$ as input.  
For centralized training, the global state $s$ can be used as input. 
The specific form of the multi-agent Q-function and the update rules depend on the chosen MARL algorithm (e.g., distributed deep Q-learning~\cite{ong2015distributed}, value decomposition methods~\cite{DBLP:conf/icml/SonKKHY19}).  
For example, in independent deep Q-learning, each agent updates its Q-network independently using its local reward $r^i$:
\begin{equation}
  \resizebox{\linewidth}{!}{$
  \mathcal{L}^i(\theta^i) = \mathbb{E}_{(o^i, a^i, r^i, o'^i) \sim \mathcal{D}^i} \left[ \left( r^i + \gamma \max_{a'^i} Q^i(o'^i, a'^i; \theta^{i-}) - Q^i(o^i, a^i; \theta^i) \right)^2 \right]
  $}
  \end{equation}
%\subsection{Key Concepts}
